Notes on Prediction Types

### 2011-06-21 docs/pert_notes/pert.tex
add species_pred_type = 3 to the enthalpy notes

\subsection{{\tt species\_pred\_type} = {\tt predict\_rhoprime\_and\_X}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{{\tt species\_pred\_type} = {\tt predict\_rhoprime\_and\_rhoX}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{{\tt species\_pred\_type} = {\tt predict\_rho\_and\_X}}

@@

\noindent Note: the various {\tt enthalpy\_pred\_type}s are only
guaranteed to work with {\tt species\_pred\_type = 1}.

@@

\begin{landscape}
\begin{table}[t]
\caption{Summary of enthalpy edge state construction}
\label{table:pred:hoverview}
\renewcommand{\arraystretch}{1.5}
{\small
\centering
\begin{tabular}{l|l|c|c|c|c}
\hline
\hline
{\tt species\_pred\_type} &   
{\tt enthalpy\_pred\_type} &
{cell-centered} &
{intermediate} &
{species quantity} &
{final $(\rho h)$} \\[-5pt]
 &
 &
{quantity predicted} &
{``enthalpy''} &
{available in} &
{edge state} \\[-5pt]
 &
 &
{in {\tt make\_edge\_scal}} &
{edge state} &
{\tt mkflux} &
 \\
\hline 
1 / {\tt predict\_rhoprime\_and\_X}  & 1 / {\tt predict\_rhohprime} &
  $(\rho h)'$ & $(\rho h)'_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
1 / {\tt predict\_rhoprime\_and\_X}  & 2 / {\tt predict\_h} &
  $h$ & $h_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left ( \rho_0^{n+\myhalf,{\rm avg}} + \rho'_\mathrm{edge} \right ) h_\mathrm{edge}$ \\
1 / {\tt predict\_rhoprime\_and\_X}  & 3 / {\tt predict\_T\_then\_rhohprime} &
  $T$ & $(\rho h)'_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
1 / {\tt predict\_rhoprime\_and\_X}  & 4 / {\tt predict\_T\_then\_h} &
  $T$ & $h_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left ( \rho_0^{n+\myhalf,{\rm avg}} + \rho'_\mathrm{edge} \right ) h_\mathrm{edge}$ \\
\hline
\hline
2 / {\tt predict\_rhoprime\_and\_rhoX}  & 1 / {\tt predict\_rhohprime} &
  $(\rho h)'$ & $(\rho h)'_\mathrm{edge}$ & 
  $(\rho X)_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
2 / {\tt predict\_rhoprime\_and\_rhoX}  & 2 / {\tt predict\_h} &
  $h$ & $h_\mathrm{edge}$ & 
  $(\rho X)_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left ( \rho_0^{n+\myhalf,{\rm avg}} + \rho'_\mathrm{edge} \right ) h_\mathrm{edge}$ \\
2 / {\tt predict\_rhoprime\_and\_rhoX}  & 3 / {\tt predict\_T\_then\_rhohprime} &
  $T$ & $(\rho h)'_\mathrm{edge}$ & 
  $(\rho X)_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
2 / {\tt predict\_rhoprime\_and\_rhoX}  & 4 / {\tt predict\_T\_then\_h} &
  $T$ & $h_\mathrm{edge}$ & 
  $(\rho X)_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left ( \rho_0^{n+\myhalf,{\rm avg}} + \rho'_\mathrm{edge} \right ) h_\mathrm{edge}$ \\
\hline
\end{tabular}
} % end \small
\end{table}
\end{landscape}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{{\tt enthalpy\_pred\_type} = {\tt predict\_rhohprime}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{{\tt enthalpy\_pred\_type} = {\tt predict\_h}}

Here we wish to construct $\left (\rho_0 + \rho'_\mathrm{edge} \right
) h_\mathrm{edge}$ by predicting $h$ to the edges.

@@

We use the same procedure described in Section \ref{Computing rho at
  edges} for computing $\rho_\mathrm{edge}$ from $\rho_0$ and
$\rho'_\mathrm{edge}$ and then multiply by $h_\mathrm{edge}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{{\tt enthalpy\_pred\_type} = {\tt predict\_T\_then\_rhohprime}}

@@

\begin{table*}[h]
\centering
\caption{EOS states in {\tt makeHfromRhoT\_edge}\newline}
\label{table:pred:EOSinputs}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{l|c|c}
\hline
\hline
{\tt species\_pred\_type} & {$\rho$ edge state} &   {$X_k$ edge state}  \\
\hline
{\tt predict\_rhoprime\_and\_X} & 
  $\rho_0^{n+\myhalf,\rm{avg}} + \rho'_\mathrm{edge}$ & 
  $(X_k)_\mathrm{edge}$ \\
{\tt predict\_rhoprime\_and\_rhoX} & 
  $\sum_k (\rho X_k)_\mathrm{edge}$ & 
  $(\rho X_k)_\mathrm{edge}/\sum_k (\rho X_k)_\mathrm{edge}$ \\
\hline
\end{tabular}
\end{table*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{{\tt enthalpy\_pred\_type} = {\tt predict\_T\_then\_h}}

Here we wish to construct $\left (\rho_0 + \rho'_\mathrm{edge} \right
) h_\mathrm{edge}$ by predicting $T$ to the edges and then converting
this to $h_\mathrm{edge}$ via the EOS.

>>>>

\subsection{Method 1: {\tt species\_pred\_type} = {\tt predict\_rhoprime\_and\_X}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Method 2: {\tt species\_pred\_type} = {\tt predict\_rhoprime\_and\_rhoX}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Method 3: {\tt species\_pred\_type} = {\tt predict\_rho\_and\_X}}

@@

\noindent Note: the various {\tt enthalpy\_pred\_type}s have only been
extensively tested with {\tt species\_pred\_type = 1}.

@@

\begin{landscape}
\begin{table}[t]
\caption{Summary of enthalpy edge state construction}
\label{table:pred:hoverview}
\renewcommand{\arraystretch}{1.5}
{\small
\centering
\begin{tabular}{l|l|c|c|c|c}
\hline
\hline
{\tt species\_pred\_type} &   
{\tt enthalpy\_pred\_type} &
{cell-centered} &
{intermediate} &
{species quantity} &
{final $(\rho h)$} \\[-5pt]
 &
 &
{quantity predicted} &
{``enthalpy''} &
{available in} &
{edge state} \\[-5pt]
 &
 &
{in {\tt make\_edge\_scal}} &
{edge state} &
{\tt mkflux} &
 \\
\hline 
1 / {\tt predict\_rhoprime\_and\_X}  & 1 / {\tt predict\_rhohprime} &
  $(\rho h)'$ & $(\rho h)'_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
1 / {\tt predict\_rhoprime\_and\_X}  & 2 / {\tt predict\_h} &
  $h$ & $h_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left ( \rho_0^{n+\myhalf,{\rm avg}} + \rho'_\mathrm{edge} \right ) h_\mathrm{edge}$ \\
1 / {\tt predict\_rhoprime\_and\_X}  & 3 / {\tt predict\_T\_then\_rhohprime} &
  $T$ & $(\rho h)'_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
1 / {\tt predict\_rhoprime\_and\_X}  & 4 / {\tt predict\_T\_then\_h} &
  $T$ & $h_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left ( \rho_0^{n+\myhalf,{\rm avg}} + \rho'_\mathrm{edge} \right ) h_\mathrm{edge}$ \\
\hline
\hline
2 / {\tt predict\_rhoprime\_and\_rhoX}  & 1 / {\tt predict\_rhohprime} &
  $(\rho h)'$ & $(\rho h)'_\mathrm{edge}$ & 
  $(\rho X)_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
2 / {\tt predict\_rhoprime\_and\_rhoX}  & 2 / {\tt predict\_h} &
  $h$ & $h_\mathrm{edge}$ & 
  $(\rho X)_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left ( \rho_0^{n+\myhalf,{\rm avg}} + \rho'_\mathrm{edge} \right ) h_\mathrm{edge}$ \\
2 / {\tt predict\_rhoprime\_and\_rhoX}  & 3 / {\tt predict\_T\_then\_rhohprime} &
  $T$ & $(\rho h)'_\mathrm{edge}$ & 
  $(\rho X)_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
2 / {\tt predict\_rhoprime\_and\_rhoX}  & 4 / {\tt predict\_T\_then\_h} &
  $T$ & $h_\mathrm{edge}$ & 
  $(\rho X)_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left ( \rho_0^{n+\myhalf,{\rm avg}} + \rho'_\mathrm{edge} \right ) h_\mathrm{edge}$ \\
\hline
\hline
3 / {\tt predict\_rho\_and\_X}  & 1 / {\tt predict\_rhohprime} &
  $(\rho h)'$ & $(\rho h)'_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
3 / {\tt predict\_rho\_and\_X}  & 2 / {\tt predict\_h} &
  $h$ & $h_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho_\mathrm{edge}$ & 
  $\rho_\mathrm{edge} h_\mathrm{edge}$ \\
3 / {\tt predict\_rho\_and\_X}  & 3 / {\tt predict\_T\_then\_rhohprime} &
  $T$ & $(\rho h)'_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
3 / {\tt predict\_rho\_and\_X}  & 4 / {\tt predict\_T\_then\_h} &
  $T$ & $h_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho_\mathrm{edge}$ & 
  $\rho_\mathrm{edge} h_\mathrm{edge}$ \\
\hline
\end{tabular}
} % end \small
\end{table}
\end{landscape}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Method 1: {\tt enthalpy\_pred\_type} = {\tt predict\_rhohprime}}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Method 2: {\tt enthalpy\_pred\_type} = {\tt predict\_h}}

Here, the construction of the interface state depends on what species 
quantities are present.  In all cases, the enthalpy state is found
by predicting $h$ to the edges.

For {\tt species\_pred\_types}: {\tt predict\_rhoprime\_and\_X} or
{\tt predict\_rhoprime\_and\_rhoX}, we wish to construct $(\rho_0 +
\rho'_\mathrm{edge} ) h_\mathrm{edge}$.

For {\tt species\_pred\_types}: {\tt predict\_rho\_and\_X}, we wish to
construct $\rho_\mathrm{edge} h_\mathrm{edge}$.

@@

{\tt species\_pred\_types}: {\tt predict\_rhoprime\_and\_X} or
{\tt predict\_rhoprime\_and\_rhoX}:\\[1mm]
%
We use the same procedure described in Section \ref{Computing rho at
  edges} for computing $\rho_\mathrm{edge}$ from $\rho_0$ and
$\rho'_\mathrm{edge}$ and then multiply by $h_\mathrm{edge}$.

\ \\
{\tt species\_pred\_types}: {\tt predict\_rho\_and\_X}:\\[1mm]
%
We already have $\rho_\mathrm{edge}$ and simply multiply by
$h_\mathrm{edge}$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Method 3: {\tt enthalpy\_pred\_type} = {\tt predict\_T\_then\_rhohprime}}

@@

\begin{table*}[h]
\centering
\caption{EOS states in {\tt makeHfromRhoT\_edge}\newline}
\label{table:pred:EOSinputs}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{l|c|c}
\hline
\hline
{\tt species\_pred\_type} & {$\rho$ edge state} &   {$X_k$ edge state}  \\
\hline
{\tt predict\_rhoprime\_and\_X} & 
  $\rho_0^{n+\myhalf,\rm{avg}} + \rho'_\mathrm{edge}$ & 
  $(X_k)_\mathrm{edge}$ \\
{\tt predict\_rhoprime\_and\_rhoX} & 
  $\sum_k (\rho X_k)_\mathrm{edge}$ & 
  $(\rho X_k)_\mathrm{edge}/\sum_k (\rho X_k)_\mathrm{edge}$ \\
{\tt predict\_rho\_and\_X} & 
  $\rho_\mathrm{edge}$ & 
  $(X_k)_\mathrm{edge}$ \\
\hline
\end{tabular}
\end{table*}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Method 4: {\tt enthalpy\_pred\_type} = {\tt predict\_T\_then\_h}}

Here, the construction of the interface state depends on what species
quantities are present.  In all cases, the enthalpy state is found by
predicting $T$ to the edges and then converting this to
$h_\mathrm{edge}$ via the EOS.

For {\tt species\_pred\_types}: {\tt predict\_rhoprime\_and\_X} or
{\tt predict\_rhoprime\_and\_rhoX}, we wish to construct $(\rho_0 +                                             \rho'_\mathrm{edge} ) h_\mathrm{edge}$.

For {\tt species\_pred\_types}: {\tt predict\_rho\_and\_X}, we wish to
construct $\rho_\mathrm{edge} h_\mathrm{edge}$.
